Sample Length at Which Block Bootstrapping is Effective for Estimation of Parameter of Time Series

### 2023-02-02 Code/NewPlots.Rmd
Manuscript Update

```{r}
graph_bts <- function(cov, theta, target, width, nrep = 1000, sizes = c(100, 500, 1000), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'theta'), level = .95) {
  n <- rep(sizes, each = length(types) * length(parameters))
  CI <- rep(types, times = length(sizes), each = length(parameters))
  t <- rep(parameters, times = length(sizes) * length(types))
  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
  UB <-sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])

  df <- data.frame(n, CI, t, cov, LB, UB)
  library(ggplot2)
  ggplot(df, aes(x = n, y = cov)) +
    geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
    geom_line() +
    geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
    facet_grid(t ~ CI)
}
```

```{r}
theta <- 0.1
target <- c(0, 1, theta)
cov <- c(mychk(sim_.1_1h, target), mychk(sim_.1_5h, target), mychk(sim_.1_1k, target))

graph_bts(cov, theta, target, width = 50)
ggsave('../Manuscript/plot_.1.pdf')
```
```{r}
theta <- 0.3
target <- c(0, 1, theta)
cov <- c(mychk(sim_.3_1h, target), mychk(sim_.3_5h, target), mychk(sim_.3_1k, target))

graph_bts(cov, theta, target, width = 25)
ggsave('../Manuscript/plot_.3.pdf')
```
```{r}
theta <- 0.5
target <- c(0, 1, theta)
cov <- c(mychk(sim_.5_1h, target), mychk(sim_.5_5h, target), mychk(sim_.5_1k, target))

graph_bts(cov, theta, target, width = 10)
ggsave('../Manuscript/plot_.5.pdf')
```

>>>>

```{r}
graph_bts <- function(cov, phi, target, width, trans = 'identity', nrep = 1000, sizes = c(100, 200, 300, 400, 500, 600), types = c('estCI', 'mbtCI', 'altCI', 'bcaCIest', 'bcaCImbt', 'bcaCIalt'), parameters = c('mu', 'sigma', 'phi'), level = .95) {
  n <- rep(sizes, each = length(types) * length(parameters))
  CI <- rep(types, times = length(sizes), each = length(parameters))
  t <- rep(parameters, times = length(sizes) * length(types))
  LB <- sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[1])
  UB <-sapply(cov, function(i) prop.test(i*nrep, nrep)$conf.int[2])

  df <- data.frame(n, CI, t, cov, LB, UB)
  library(ggplot2)
  ggplot(df, aes(x = n, y = cov)) +
    geom_hline(yintercept = level, linetype = 'dashed', color = 'orange') + 
    geom_line() +
    geom_errorbar(aes(ymin=LB, ymax = UB), colour="black", width = width) +
    facet_grid(factor(t, levels = parameters) ~ factor(CI, levels = types)) +
    scale_y_continuous(trans=trans)
}
```

```{r}
phi <- -.4
target <- c(0, 1, phi)
cov <- c(mychk(sim_n.4_1h, target), mychk(sim_n.4_2h, target), mychk(sim_n.4_3h, target), mychk(sim_n.4_4h, target), mychk(sim_n.4_5h, target), mychk(sim_n.4_6h, target))

graph_bts(cov, phi, target, width = 25, trans = 'probit')
ggsave('../Manuscript/figures/plot_n.4.pdf')
```
```{r}
phi <- -.2
target <- c(0, 1, phi)
cov <- c(mychk(sim_n.2_1h, target), mychk(sim_n.2_2h, target), mychk(sim_n.2_3h, target), mychk(sim_n.2_4h, target), mychk(sim_n.2_5h, target), mychk(sim_n.2_6h, target))
graph_bts(cov, phi, target, width = 25, trans = 'exp')
ggsave('../Manuscript/figures/plot_n.2.pdf')
```

```{r}
phi <- 0
target <- c(0, 1, phi)
cov <- c(mychk(sim_0_1h, target), mychk(sim_0_2h, target), mychk(sim_0_3h, target), mychk(sim_0_4h, target), mychk(sim_0_5h, target), mychk(sim_0_6h, target))
graph_bts(cov, phi, target, width = 25)
ggsave('../Manuscript/figures/plot_0.pdf')
```
```{r}
phi <- .2
target <- c(0, 1, phi)
cov <- c(mychk(sim_.2_1h, target), mychk(sim_.2_2h, target), mychk(sim_.2_3h, target), mychk(sim_.2_4h, target), mychk(sim_.2_5h, target), mychk(sim_.2_6h, target))
graph_bts(cov, phi, target, width = 25)
ggsave('../Manuscript/figures/plot_.2.pdf')
```
```{r}
phi <- .4
target <- c(0, 1, phi)
cov <- c(mychk(sim_.4_1h, target), mychk(sim_.4_2h, target), mychk(sim_.4_3h, target), mychk(sim_.4_4h, target), mychk(sim_.4_5h, target), mychk(sim_.4_6h, target))

graph_bts(cov, phi, target, width = 25, trans = 'probit')
ggsave('../Manuscript/figures/plot_.4.pdf')
```

### 2023-02-02 Code/simulation.Rmd
Manuscript Update

@@

@@

@@

>>>>

```{r ar = -.4, n = 100}
n <- 100
blksize <- 5
phi <- -.4
target <- c(0, 1, phi)
set.seed(1234)
sim_n.4_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.4_1h,"../Data/Raw/sim_n.4_1h.csv", row.names = FALSE)
mychk(sim_n.4_1h, target)
```

```{r ar = -.4, n = 200}
n <- 200
blksize <- 6
phi <- -.4
target <- c(0, 1, phi)
set.seed(2345)
sim_n.4_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.4_2h,"../Data/Raw/sim_n.4_2h.csv", row.names = FALSE)
mychk(sim_n.4_2h, target)
```

```{r ar = -.4, n = 300}
n <- 300
blksize <- 7
phi <- -.4
target <- c(0, 1, phi)
set.seed(3456)
sim_n.4_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.4_3h,"../Data/Raw/sim_n.4_3h.csv", row.names = FALSE)
mychk(sim_n.4_3h, target)
```

```{r ar = -.4, n = 400}
n <- 400
blksize <- 7
phi <- -.4
target <- c(0, 1, phi)
set.seed(4567)
sim_n.4_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.4_4h,"../Data/Raw/sim_n.4_4h.csv", row.names = FALSE)
mychk(sim_n.4_4h, target)
```

```{r ar = -.4, n = 500}
n <- 500
blksize <- 8
phi <- -.4
target <- c(0, 1, phi)
set.seed(5678)
sim_n.4_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.4_5h,"../Data/Raw/sim_n.4_5h.csv", row.names = FALSE)
mychk(sim_n.4_5h, target)
```

```{r ar = -.4, n = 600}
n <- 600
blksize <- 9
phi <- -.4
target <- c(0, 1, phi)
set.seed(6789)
sim_n.4_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.4_6h,"../Data/Raw/sim_n.4_6h.csv", row.names = FALSE)
mychk(sim_n.4_6h, target)
```

```{r ar = -.2, n = 100}
n <- 100
blksize <- 5
phi <- -.2
target <- c(0, 1, phi)
set.seed(1234)
sim_n.2_1h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.2_1h,"../Data/Raw/sim_n.2_1h.csv", row.names = FALSE)
mychk(sim_n.2_1h, target)
```

```{r ar = -.2, n = 200}
n <- 200
blksize <- 6
phi <- -.2
target <- c(0, 1, phi)
set.seed(2345)
sim_n.2_2h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.2_2h,"../Data/Raw/sim_n.2_2h.csv", row.names = FALSE)
mychk(sim_n.2_2h, target)
```

```{r ar = -.2, n = 300}
n <- 300
blksize <- 7
phi <- -.2
target <- c(0, 1, phi)
set.seed(3456)
sim_n.2_3h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.2_3h,"../Data/Raw/sim_n.2_3h.csv", row.names = FALSE)
mychk(sim_n.2_3h, target)
```

```{r ar = -.2, n = 400}
n <- 400
blksize <- 7
phi <- -.2
target <- c(0, 1, phi)
set.seed(4567)
sim_n.2_4h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.2_4h,"../Data/Raw/sim_n.2_4h.csv", row.names = FALSE)
mychk(sim_n.2_4h, target)
```

```{r ar = -.2, n = 500}
n <- 500
blksize <- 8
phi <- -.2
target <- c(0, 1, phi)
set.seed(5678)
sim_n.2_5h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.2_5h,"../Data/Raw/sim_n.2_5h.csv", row.names = FALSE)
mychk(sim_n.2_5h, target)
```

```{r ar = -.2, n = 600}
n <- 600
blksize <- 9
phi <- -.2
target <- c(0, 1, phi)
set.seed(6789)
sim_n.2_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_n.2_6h,"../Data/Raw/sim_n.2_6h.csv", row.names = FALSE)
mychk(sim_n.2_6h, target)
```

@@

```{r ar = 0, n = 600}
n <- 600
blksize <- 9
phi <- 0
target <- c(0, 1, phi)
set.seed(6789)
sim_0_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_0_6h,"../Data/Raw/sim_0_6h.csv", row.names = FALSE)
mychk(sim_0_6h, target)
```

@@

```{r ar = .2, n = 600}
n <- 600
blksize <- 9
phi <- .2
target <- c(0, 1, phi)
set.seed(6789)
sim_.2_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.2_6h,"../Data/Raw/sim_.2_6h.csv", row.names = FALSE)
mychk(sim_.2_6h, target)
```

@@

```{r ar = .4, n = 600}
n <- 600
blksize <- 9
phi <- .4
target <- c(0, 1, phi)
set.seed(6789)
sim_.4_6h <- replicate(nrep, do1rep(n, phi, mystat, blksize))
write.csv(sim_.4_6h,"../Data/Raw/sim_.4_6h.csv", row.names = FALSE)
mychk(sim_.4_6h, target)
```

### 2023-02-02 Manuscript/manuscript.tex
Manuscript Update

Block bootstrapping is a method that can be used to estimate a parameter of an AR(1) process. Suppose that one wants to estimate a parameter or parameters $\theta$ of an AR(1) process: 
\[X_{t} = \mu + \epsilon_{t} + \phi*X_{t-1}.\] The first step is to generate a sample of length $n$ from the process. An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample. A pseudo-estimate $\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample. The mean $\bar\theta_n^*$ of many (typically 1000) replicate $\hat\theta_n^*$ can also be computed. Lastly, for each $\hat\theta_n^*$, $\delta = \hat\theta_n^* - \hat{\theta}_{n}$ and $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.

@@

	Both of these intervals are good at recovering the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as $n$ increases. A potential solution to this issue is to center the intervals around either $\hat{\theta}_{n}$ or $\bar\theta_n^*$. To do this, the distribution of $\delta$ or $\delta^*$ should be considered. A percentile interval centered around $\hat{\theta}_{n}$ takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\] 
A percentile interval centered around $\bar\theta_n^*$ takes the form: 
\[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\]
An alternative is an interval of the form:
\[ [\hat{\theta}_{n} - \delta^*_{1 - \alpha/2}, \hat{\theta}_{n} - \delta^*_{\alpha/2}],\] 
which is equivalent to:
\[ [\hat{\theta}_{n} + \bar\theta_n^*- \hat\theta_{n, \alpha/2}^*, \hat{\theta}_{n} + \bar\theta_n^* - \hat\theta_{n, 1 - \alpha/2}^*],\] 
and therefore is also equivalent to:
\[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] 
Thus, the interval is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.

This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1}, \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
A BCA interval centered around $\bar\theta_n^*$ takes the form: 
\[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\]
An alternative is an interval of the form:
\[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}],\]

@@

R has a built in function that allows you to simulate an AR(1) process, for which one can set the theoretical $\phi$. For the purposes of this study, $\mu$ should be fixed at 0, and the standard deviation of the process $\sigma_{x}$ should be fixed at 1. By default, the standard deviation of the error term $\sigma_{\epsilon}$ is 1, so the observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:

\[X_{t} = \epsilon_{t} + \phi*X_{t-1}.\]
\[Var(X_{t}) = Var(\epsilon_{t} + \phi*X_{t-1})\]
\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2*\sigma^2_{x}\]
\[\sigma^2_{x}(1 - \phi^2) = \sigma^2_{\epsilon}\]
\[\sigma_{\epsilon} = \sigma_{x}\sqrt{1 - \phi^2}\]

The only parameter of the AR(1) process that was varied was $\phi$, as the temporal dependence affects the performance of block bootstrap. $\phi$ = 0 (a standard normal distribution), 0.2, and 0.4 were used in this study.

As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process. In this study, $\theta$ is composed of the target parameters $\mu$, $\sigma_{x}$, and $\phi$. From a sample of length $n$, six block bootstrap 95\% confidence intervals can be constructed for each target parameter: ....

@@

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_0}
  \caption{At $\phi = 0$, all intervals covered $\mu$ correctly at $n = 500$. All but three intervals seem to cover $\phi$ generally well for $n = 300$. The alternate percentile interval slightly under-covers $\phi$ for all sample lengths observed. The BCA interval centered around $\hat{\theta}_{n}$ significantly under-covers $\phi$ and the percentile interval centered around $\bar\theta_n^*$ over-covers $\phi$. All intervals seem to cover $\sigma$ generally well for n = 500 except for the $\hat{\theta}_{n}$-centered BCA interval, which slightly under-covers $\sigma$ for all sample lengths observed, and the  $\bar\theta_n^*$-centered BCA interval, which also under-covers $\sigma$.}
  \label{fig:plot_0}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.2}
  \caption{At $\phi = .2$, all intervals covered $\mu$ correctly at $n = 300$ and $n = 400$. The alternate percentile interval and the $\hat{\theta}_{n}$-centered percentile interval cover $\phi$ well at $n = 500$. The $\bar\theta_n^*$-centered BCA interval slightly under-covers $\phi$ for all sample lengths observed. The alternate BCA interval under-covers $\phi$, and its performance deteriorates as $n$ increases, as does the $\bar\theta_n^*$-centered percentile interval but with lower coverage rates and more noticeable deterioration. The $\hat{\theta}_{n}$-centered BCA interval significantly under-covers $\phi$, although there is no clear deterioration.}
  \label{fig:plot_.2}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.4}
  \caption{At $\phi = .4$,}
  \label{fig:plot_.4}
\end{figure}

@@

This study finds that as the AR coefficient increases, the sample size necessary for effective block bootstrap estimation must be larger. When implementing the block bootstrap method to estimate the mean or variance of an autoregressive process, the non-moving method and moving method perform about the same. However, when estimating the AR(1) coefficient, the non-moving method performs noticeably worse than the moving method, which still covers the coefficient poorly when theta is greater than 0. Whereas the performance improves as sample length increases when the target is the mean or variance, the performance decays as sample length increases when the target is the AR(1) coefficient.

>>>>

Block bootstrapping is a method that can be used to estimate a parameter of serially dependent data. Suppose that one wants to estimate a parameter or parameters $\theta$ of a population. The first step is to generate a sample of length $n$ from the population. An estimate of the parameter $\hat{\theta}_{n}$ can be computed from this sample. A pseudo-estimate $\hat\theta_n^*$ can be computed from a bootstrapped pseudo-sample. The mean $\bar\theta_n^*$ of many (typically 1000) replicate $\hat\theta_n^*$ can also be computed. Lastly, for each $\hat\theta_n^*$, $\delta = \hat\theta_n^* - \hat{\theta}_{n}$ and $\delta^* = \hat\theta_n^* - \bar\theta_n^*$ can be computed.

@@

	Both of these intervals are good at recovering the mean and standard deviation of a temporally dependent process, but their coverage of the temporal dependence deteriorates as $n$ increases. A potential solution to this issue is to center the intervals around either $\hat{\theta}_{n}$ or $\bar\theta_n^*$. To do this, the distribution of $\delta$ or $\delta^*$ should be considered. A percentile interval centered around $\hat{\theta}_{n}$ ($CI_{\hat{\theta}_{n}}$) takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha/2}, \hat{\theta}_{n} + \delta^*_{1 - \alpha/2}].\] 
A percentile interval centered around $\bar\theta_n^*$ ($CI_{\bar\theta_n^*}$) takes the form: 
\[ [\bar\theta_n^* + \delta_{\alpha/2}, \bar\theta_n^* + \delta_{1 - \alpha/2}].\]
An alternative is an interval of the form:
\[ [\hat{\theta}_{n} - \delta^*_{1 - \alpha/2}, \hat{\theta}_{n} - \delta^*_{\alpha/2}],\] 
which is equivalent to:
\[ [\hat{\theta}_{n} + \bar\theta_n^*- \hat\theta_{n, \alpha/2}^*, \hat{\theta}_{n} + \bar\theta_n^* - \hat\theta_{n, 1 - \alpha/2}^*],\] 
and therefore is also equivalent to:
\[ [\bar\theta_n^* - \delta_{1 - \alpha/2}, \bar\theta_n^*- \delta_{\alpha/2}].\] 
Thus, the interval ($CI_{\hat{\theta}_{n}, \bar\theta_n^*}$) is centered around both $\hat{\theta}_{n}$ and $\bar\theta_n^*$.

This centering procedure can also be applied to a BCA interval. A BCA interval centered around $\hat{\theta}_{n}$ ($CI_{BCA, \hat{\theta}_{n}}$) takes the form:
\[ [\hat{\theta}_{n} + \delta^*_{\alpha_1}, \hat{\theta}_{n} + \delta^*_{\alpha_2}].\] 
A BCA interval centered around $\bar\theta_n^*$ ($CI_{BCA, \bar\theta_n^*}$) takes the form: 
\[ [\bar\theta_n^* + \delta_{\alpha_1}, \bar\theta_n^* + \delta_{\alpha_2}].\]
An alternative (($CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$) is an interval of the form:
\[ [\hat{\theta}_{n} - \delta^*_{\alpha_2}, \hat{\theta}_{n} - \delta^*_{\alpha_1}]\]

Thus there are three possible ways to center an interval: $CI_{\hat{\theta}_{n}}$, $CI_{\bar\theta_n^*}$, $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$, and three additional intervals which use bias-correction and acceleration to determine the percentiles for the critical values: $CI_{BCA, \hat{\theta}_{n}}$, $CI_{BCA, \bar\theta_n^*}$, $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$.

@@

R has a built in function that allows you to simulate an AR(1) process, for which one can set the theoretical $\phi$. By default, the mean of the process $\mu$ is 0 and the standard deviation of the error term $\sigma_{\epsilon}$ is 1. For the purposes of this study, the standard deviation of the process $\sigma_{x}$ should be controlled at 1. The observations can be multiplied by $\sqrt{1 - \phi^2}$ so that the new theoretical $\sigma_{x}$ is equivalent to 1, as shown below:

\[X_{t} = \epsilon_{t} + \phi X_{t-1}.\]
\[Var(X_{t}) = Var(\epsilon_{t} + \phi X_{t-1})\]
\[\sigma^2_{x} = \sigma^2_{\epsilon} + \phi^2 \sigma^2_{x}\]
\[\sigma^2_{x}(1 - \phi^2) = 1\]
\[\sigma_{x}\sqrt{1 - \phi^2} = 1\]

The experimental factor of this study was $\phi$, as the temporal dependence affects the performance of block bootstrap. $\phi = -0.4 -0.2,$ and $0$ (a standard normal distribution)$, 0.2, and 0.4$ were used in this study.

As described in the last section, the block bootstrap method can be used to estimate a parameter $\theta$ of an AR(1) process. In this study, $\theta$ is composed of the target parameters $\mu = 0$, $\sigma_{x}$, and $\phi$. From a sample of length $n$, six block bootstrap 95\% confidence intervals can be constructed for each target parameter: ....

@@

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_n.4}
  \caption{At $\phi = -.4$, all intervals covered $\mu$ correctly as low as $n = 100$. $CI_{\hat{\theta}_{n}}$, $CI_{\bar\theta_n^*}$, $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$, and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ seem to cover $\sigma$ well at $n = 600$. $CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ undercover $\sigma$, but there is no clear pattern of deterioration of coverage, so increasing $n$ will eventually result in good coverage. $CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ are the only two intervals that cover $\phi$ well with no deterioration, and this is true as low as $n = 200$. The other types of intervals greatly under-cover $\sigma$ and there is a clear pattern of deterioration of coverage.}
  \label{fig:plot_n.4}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_n.2}
  \caption{At $\phi = -.2$, all intervals covered $\mu$ correctly as low as $n = 100$. All intervals seem to cover $\sigma$ generally well at $n = 600$, although $CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ have noticeably lower coverage rates. $CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ are the only two intervals that cover $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$.  $CI_{\bar\theta_n^*}$ and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ cover $\phi$ well at $n = 100$, but the coverage deteriorates as $n$ increases. $CI_{BCA, \bar\theta_n^*}$ slightly under-covers $\phi$, and there is a slight coverage deterioration trend as $n$ increases. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$, and there is a coverage deterioration trend as $n$ increases.}
  \label{fig:plot_n.2}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_0}
  \caption{At $\phi = 0$, all intervals covered $\mu$ correctly as low as $n = 500$. $CI_{\hat{\theta}_{n}}$, $CI_{\bar\theta_n^*}$, $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$, and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ seem to cover $\sigma$ well as low as $n = 500$. $CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ slightly undercover $\sigma$, but there is no clear pattern of deterioration of coverage, so increasing $n$ will eventually result in good coverage. $CI_{\hat{\theta}_{n}}$, $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$, $CI_{BCA, \bar\theta_n^*}$, and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ seem to cover $\phi$ generally well at $n = 600$, but $CI_{\bar\theta_n^*}$ over-covers $\phi$ with a slight coverage deterioration trend as $n$ increase, and $CI_{BCA, \bar\theta_n^*}$ under-covers $\phi$, although there is no clear coverage deterioration.}
  \label{fig:plot_0}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.2}
  \caption{At $\phi = .2$, all intervals covered $\mu$ correctly as low as $n = 300$. All intervals except for $CI_{BCA, \bar\theta_n^*}$ seem to cover $\sigma$ generally well at $n = 600$. However, $CI_{BCA, \bar\theta_n^*}$ shows no clear pattern of coverage deterioration, so increasing $n$ will eventually result in good coverage. $CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ are the only two intervals that cover $\phi$ well with no deterioration of coverage, and this is true as low as $n = 200$. $CI_{BCA, \bar\theta_n^*}$ slightly under-covers $\phi$ with no clear deterioration. $CI_{\bar\theta_n^*}$ and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ under-cover $\phi$ with a clear coverage deterioration trend as $n$ increases. $CI_{BCA, \hat{\theta}_{n}}$ greatly under-covers $\phi$ with no clear coverage deterioration.}
  \label{fig:plot_.2}
\end{figure}

\begin{figure}[tbp]
\caption{}
  \centering
  \includegraphics[width=\textwidth]{figures/plot_.4}
  \caption{At $\phi = .4$, all intervals seem to cover $\mu$ generally well at $n = 600$, although $CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ have slightly higher coverage rates. $CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ cover $\sigma$ well as low as $n = 400$, $CI_{BCA, \bar\theta_n^*}$ and $CI_{BCA, \hat{\theta}_{n}, \bar\theta_n^*}$ slightly under-cover $\sigma$, and $CI_{BCA, \hat{\theta}_{n}}$ and $CI_{BCA, \bar\theta_n^*}$ more noticeable under-cover $\sigma$. For all intervals, there is not sign of coverage deterioration, indicating that increasing $n$ will eventually result in proper coverage. $CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ are the only two intervals that cover $\phi$ well with no deterioration of coverage, and this is true as low as $n = 300$. The other intervals greatly under-cover $\phi$ with a clear coverage deterioration trend as $n$ increases.}
  \label{fig:plot_.4}
\end{figure}

Only $CI_{\hat{\theta}_{n}}$ and $CI_{\hat{\theta}_{n}, \bar\theta_n^*}$ managed to solve the deterioration problem with respect to recovering $\phi$, indicating that these intervals should be used as opposed to the other types when estimating $\phi$.

@@

The motivation for this study is what is a good enough sample size for block bootstrap.
